Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-22 presentation/presentation.tex
Change graph extension to eps
Tried to add plots to the presentation, did not manage.
Continue presentation
some minor changes to the content.

graph with log-deviations and aggregates 
  \centering{\includegraphics[scale=0.30]{eq18}}

@@

	\item {
Looking at the distribution of capital holdings gives us an even better picture.
	}

@@

distributional plot 
  \centering{\includegraphics[scale=0.30]{eq18}}

@@

\begin{itemize} 
	\item {
We saw that the policy change has a different effect on the unemployed and the employed. 
}
	\item {
Hence, we will now look at the different variables, to get an even better image.
}
\end{itemize}

@@

big subplot with all the variables
  \centering{\includegraphics[scale=0.30]{eq18}}

>>>>

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.5]{log-deviation}}

@@

	\item {
Yet it is not clear, if unemployed and employed are affected differently. 
	}

@@

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.5]{distribution}}

@@

  \centering{\includegraphics[scale=0.5]{meanandmedian}}

@@

\begin{itemize}

	\item {
Generally speaking, the unemployed and employed decrease capital holdings. 
}
	\item {
 When UI increase, differences between unemployed and employed are reduced, however, within-group inequality increases.
}
	\item {
Somewhat puzzling, at some point the $mean_{ue}$ starts to increase again.
}
	\item {
There seem to be different forces operating. 
}

  \centering{\includegraphics[scale=0.30]{parameters}}

  \centering{\includegraphics[scale=0.30]{parameters_sigma}}
